\titleNameLong{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
tweaked title

\newcommand{\titleNameLong}{General-Purpose GPUs and the Challenges of Efficient
Parallel Processing of Heterogeneous Applications}

\newcommand{\titleNameShort}{GPGPU and the Challenges of Efficient
Parallel Processing of Heterogeneous Applications}

>>>>

\newcommand{\titleNameLong}{General-Purpose Computing on GPUs and Efficient Parallel
Processing of Heterogeneous Applications}

\newcommand{\titleNameShort}{GPGPU and Efficient Parallel Processing of
Heterogeneous Applications}
